### 2009-11-19 doc/manuals/janitor/tex_introduction/introduction.tex
Yet another review with a few rewordings, reformatting.

Janitor is a service for the automated installation of runtime environment for grid computing elements.
It is addressed transparently via the A-REX service for job submission but can also be used as a standalone tool.

@@

A major motivation for grid projects is to stimulate new communities to adopt computational grids for their
causes. From the current grid user's viewpoint, the admission of users of a very different education will
suddenly impose difficulties in the communication between site maintainers. One will not even understand
the respective other side's research aims. Hence, the proper installation of non-standard software (Runtime
Environments) is not guaranteed and the priorities of manual labour will be mostly disjunctive.

@@

An automation of the software installation, referred to as dynamic Runtime Environments, seems the only
approach to use the computational grid to its full potential. Components of workflows shall be spawned
as jobs in a computational grid using dynamic Runtime Environments rather than accessing a web service
at one particular machine that is shared amongst all users.
The grid introduces an extra level of parallelism that web services cannot provide. The demands for short
response times and the heterogeneous education of site-administrators on a grid demand an automatism for
the installation of software and databases without manual interference~\cite{BAYER_2007}.

@@

This document first dedicates a chapter on how to set-up the Janitor locally. It is followed by a chapter that gives furhter instructions on how to 
use the Janitor with A-REX and/or without A-REX. Afterwards, in the third chapter, the maintenance of the program will be presented, 
which is basically covering the method how to prepare new runtime environments. Deeper insights on the design of the Janitor will 
be given by the forth chapter. The document ends with an outlook to anticipated future developments and opportunities.

>>>>

The Janitor is a service for an automated installation of runtime
environments (RTEs) for grid computing elements.  It is addressed
transparently via the A-REX service for job submission but can also be
used as a standalone tool.

@@

A major motivation for grid projects is to stimulate new communities
to adopt the technology to start sharing their resources. From the
current grid user's viewpoint, the admission of users of a very different
education will suddenly impose difficulties in the communication between
site maintainers. One will not even understand the respective other side's
research aims. Hence, the proper installation of non-standard software
(runtime environments, RTEs) is not guaranteed. And the available time for
manual labour plus self-education is scarse.

@@

An automation of the software installation, referred to as dynamic
Runtime Environments (dRTEs), seems the only approach to use the
computational grid to its full potential. Components of workflows
shall be spawned as jobs in a computational grid using dRTEs rather
than accessing a web service at one particular machine that is shared
amongst all users.  The grid introduces an extra level of parallelism
that web services cannot provide. The demands for short response times
and the heterogeneous education of site-administrators on a grid demand
an automatism for the installation of software and databases without
manual interference~\cite{BAYER_2007}.

@@

This document first dedicates a chapter on how to set-up the Janitor
locally. It is followed by a chapter that gives further instructions on
how to use the Janitor with A-REX and/or without A-REX. Afterwards, in the
third chapter, the maintenance of the program will be presented, which is
basically covering the method how to prepare new dRTEs. Deeper insights on
the design of the Janitor will be given by the forth chapter. The document
ends with an outlook to anticipated future developments and opportunities.
